---
title       : Predict Child's Height using Parent's Height
subtitle    : 
author      : Banarasi Tippa
job         : Database Engineer
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## Dataset details

1.  This dataset was tabulated by Galton in 1885  

2.  Dataset has two variables child and parent

3.  Child - Child's height

4.  Parent - the "midparent" height, an average of fathers height and 1.08 time the mother's

--- .class #id 
## Lets look at the dataset

```{r echo=FALSE}
require(UsingR)
require(ggplot2)
```

```{r }
data(galton)
str(galton)
```

--- .class #id 

## Model Creation

```{r }
fit<-lm(child~parent,galton)
#summary(fit)
coef(fit)
```
<b> Model : 

child height = `r coef(fit)[1] ` + parent * `r coef(fit)[2] ` </b>

--- .class #id 
## Use the model to predict

Lets see what's the child's height given parent's height = 70

```{r, fig.height=5, fig.width=5}
y<-predict(fit,newdata=data.frame(parent=70))
ggplot(galton,aes(parent,child))+geom_point()+geom_smooth(method="glm",col="steelblue")+
        geom_point(aes_string(x=70,y=y), color="red",shape=8,size=5)+
  labs(title=paste("Estimated Child Height :",y))
```
